Modular flow and holographic entanglement entropy in cutoff AdS

### 2021-08-07 alpha/CutoffModularFlow/notes.tex
Clean up the notes on modular flow, more

\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China\ \,\ccbyncsajp}

@@

\addtocounter{section}{-1}
\begin{itemize}[nosep]
\item add black hole spectrum 
\item geometric picture
\item maybe consider later: SSA 
\item maybe consider later: finite size effect  
\end{itemize}

\section{Conventions}
	We try to follow the conventions of the TsT paper \textcite{Apolo:2019zai}. 
	\begin{itemize}
	\item Lightcone coordinates: $u,v = x\pm t$, similar to \cite{Apolo:2019zai}. This convention has the following features:

@@

\section{$T \bar T$ deformation and cutoff AdS}
In this section we first review the holographic duality between $T\bar T$ deformed CFT$_2$ and Einstein gravity on asymptically AdS$_3$ spacetime with a finite cutoff,  and then we use the covariant phase space method to calculate the gravitational charges for BTZ black holes with finite cutoff and show that the black hole spectrum matches that of  $T\bar T$ deformed CFT$_2$.

\subsection{Black spectrum from gravitional charges}
	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.

@@

\subsubsection*{Covariant charges}

@@

\subsubsection*{Killing vectors}

@@

	Alternatively, note that we can perform a coordinate transformation 
	 % 
	 \eq{
	 \til{t}  = \frac{\sqrt{f(r_c)}}{r_c} t, \qquad \qquad \til{\phi} = \phi + \frac{4 G J }{r_c^2}t,
	 }
	 %
	to turn the induced metric~\eqref{inducedmetric} into the Minkowski metric,
	  %
	  \eq{
	  ds^2_{c} = r_c^2 \big (- d\til{t}^2 + d \til{\phi}^2 \big ), \label{mink}
	  }
	with the identifications of the original coordinates left intact, i.e.
	  %
	  \eq{
	  (\til{t},\,\til{\phi}) \sim (\tilde{t},\,\til{\phi} + 2 \pi).
	  }
	  %
	We thus find that the Killing vector $\xi_c$ is, up to a normalization, nothing but the generator of time translations in a locally nonrotating frame~\cite{Misner:1974qy},
	  %
	  \eq{
	  \xi_c  = \frac{r_c}{\sqrt{f(r_c)}} \bigg (\p_t - \frac{4 G J}{r_c^2} \p_{\phi} \bigg ) = \p_{\tilde{t}}. \label{xi1}
	  }
	  %

	The Killing vector~\eqref{xi1} satisfies the following properties:
	 %
	 \begin{enumerate}
	 \item[(i)] it leads to integrable charges, see eq.~\eqref{quasilocalcharge2};
	 \item[(ii)] its normalization is background-independent and proportional to $r_c^2$;
	 \item[(iii)] it measures the energy of a locally nonrotating observer in the orthonormal frame;
	 \item[(iv)] it reduces to the Killing vector measuring the total (ADM) energy when $r_c \to \infty$.
	 \end{enumerate}

\subsubsection*{Quasilocal energy}

@@

\section{Entanglement in the boundary story}
\subsection{Review of entanglement at zero temperature}

\subsection{Entanglement entropy at finite temperature}

\newcommand{\lp}{\ensuremath{l_p}}
\newcommand{\halfL}{\ensuremath{\frac{L}{2}}}

	One can use the method in \cite{Lewkowycz:2019xse} to calculate the entanglement entropy in the thermal case and finite size case from the field theory side. The Rindler transformation from the domain of dependence of the interval $(-\lp,\lp)$ on the plane to the sphere is
	\begin{equation}
	t=\lp\frac{\sin\theta \sinh(\tau/\lp)}{1+\sin\theta \cosh(\tau/\lp)},\ \  x=\lp\frac{\cos\theta}{1+\sin\theta\cosh(\tau/\lp)}
	\label{eq:rindler_sphere}
	\end{equation}
	the conformal factor reads,
	\begin{equation}
	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/\lp)}
	\end{equation}
	At the endpoints, it becomes $1$. From the discussion in \cite{Lewkowycz:2019xse}, the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy. Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters. If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $x = \pm \lp$, since the $T\bar T$ deformed theory also admits these symmetries.

	Now let's consider the thermal case. We will make use of two successive conformal maps: first we map the thermal cylinder to the plane, and then we use \eqref{eq:rindler_sphere} to map the plane to the sphere. 
	The conformal transformation from the thermal cylinder to the plane reads,
	\begin{equation}
	z=\frac{\beta}{2\pi}\,e^{\frac{2\pi}{\beta} w},
%	\ \ \ \kappa=\frac{2\pi}{\beta}
	\end{equation} 
	where $z = x + it$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
	\begin{equation}
	w\sim w+i\beta
	\end{equation}
	The endpoints of the interval on the thermal cylinder is
	\begin{equation}
	w=\pm \halfL
	\end{equation} 
%	The length of the interval is $L=2l$. 
	Under the conformal map, the endpoints on the plane is
	\begin{equation}
	\frac{\beta}{2\pi}e^{\pm \frac{2\pi}{\beta} \frac{L}{2}}
	\end{equation}
	the length is $\frac{\beta}{\pi}\sinh(\halfL \frac{2\pi}{\beta})$, so one can use translations and rotations to map the endpoints to $x = \pm\lp$ on the plane, where
	\begin{equation}
	l_p=\frac{\beta}{2\pi}\sinh(\halfL \frac{2\pi}{\beta})
	\end{equation}
	The conformal factor is
	\begin{equation}
	e^{\frac{2\pi}{\beta}(w+\bar{w})}
	\end{equation}
	Note that compared to the usual map from cylinder to plane $z=e^{\frac{2\pi}{\beta} w}$, we put the overall scaling factor $\frac{\beta}{2\pi}$ to make sure that the conformal factor at the endpoints is $1$.

	From \cite{Donnelly:2018bef}, the entanglement entropy for zero temperature is
	\begin{equation}
	S(L)=\frac{c}{3} \arcsinh \frac{\lp}{a}
	\end{equation}
	where
	\begin{equation}
	a^2=\frac{\mu c}{12}
	\end{equation}
	The $C$-function reads,
	\begin{equation}
	C(L)=L S'(L = 2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
	\end{equation}
	Now in the thermal case, $l_p\rightarrow \frac{\beta}{2\pi}\sinh(\halfL \frac{2\pi}{\beta})$
	\begin{equation}
	S_t=\frac{c}{3}\arcsinh \pqty{
			\frac{1}{\kappa a}\sinh(\halfL \frac{2\pi}{\beta})
		}
	\end{equation}
	\sidenote{which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{} [This is now the first non-trivial result of the paper. This comment should be moved to later.]}

	------------

	Now consider the finite size case, the conformal transformation is,
	\begin{equation}
	z=\frac{1}{ir_1}e^{iwr_1},\quad
		r_1 = \frac{2\pi}{\sidenote{R}}
	\end{equation}
	where $w$ is the cylinder coordinate, and $R$ is the \textit{spatial} size of the cylinder:
	\begin{equation}
	w\sim w+ R
	\end{equation}
	The endpoints of the interval are 
	\begin{equation}
	w\pm l
	\end{equation}
	The conformal factor is
	\begin{equation}
	e^{ir_1(w+\bar{w})}
	\end{equation}
	which is $1$ at the endpoints. The plane length reads,
	\begin{equation}
	l_p=\frac{1}{r_1}\sin lr_1
	\end{equation}
	So the final result is
	\begin{equation}
	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
	\end{equation}

	The global AdS reads,
	\begin{equation}
	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
	\end{equation}
	\begin{equation}
	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
	\end{equation}
	\begin{equation}
	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
	\end{equation}
	Compared to the planer BTZ,
	\begin{equation}
	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
	\end{equation}
	For the holographic entanglement entropy
	\begin{equation}
	r_1\rightarrow ir_1
	\end{equation}
	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
	\begin{equation}
	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
	\end{equation}

\pagebreak
\subsection{Boundary modular flows}

@@

	For simplicity, we now restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{{\tilde L}}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval. For a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
	\begin{equation}
		x_\pm = \pm \frac{{\tilde L}}{2} \cosh \theta,
	\quad
		t_\pm = \pm \frac{{\tilde L}}{2} \sinh \theta,
	\end{equation}
	Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi_\mrm{CFT} &= \frac{2\pi}{{\tilde L}} \bigg\{
			\pqty{
				\pqty{
					(\tfrac{{\tilde L}}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty{
				\pqty{
					(\tfrac{{\tilde L}}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{gather}
	Suppose the interval $\mcal{A}$ lies on the constant $t = 0$ slice; around the constant $t = 0$ slice, the modular flow becomes:
	\begin{equation}
		\xi_\mrm{CFT}|_{t = 0} 
		= \frac{2\pi}{{\tilde L}}
			\pqty{
				(\tfrac{{\tilde L}}{2})^2
				- x^2
			} \,\pdd{t}
	\end{equation}

@@

	For example, for a single interval in CFT$_2$,
	\begin{equation}
		\beta(x)
		= \frac{2\pi}{{\tilde L}}
			\pqty{
				\pqty{\tfrac{{\tilde L}}{2}}^2
				- x^2
			} \,\pdd{t}
	\end{equation}
	\begin{equation}
	S= \frac{c}{3} \int_{-{\tilde L}/2}^{{\tilde L}/2}
			\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx,
	\end{equation}
	The indefinite integral $
		\int \frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
		= \mop{arctanh}\frac{2x}{{\tilde L}}
%		\rightarrow\mrm{CFT}
	$ diverges as $x\rightarrow {\tilde L}/2$, so one needs a cutoff:
	\begin{equation}
	S=\frac{c}{3}\int_{-{\tilde L}/2+\epsilon}^{{\tilde L}/2-\epsilon}
		\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
	=\frac{2c}{3} \mop{arctanh} \pqty{
			1-\frac{2\epsilon}{{\tilde L}}
		}
	\end{equation}
	As $\epsilon\rightarrow 0$,
	\begin{equation}
		\mop{arctanh} \pqty{
			1-\frac{2\epsilon}{{\tilde L}}
		}\rightarrow \frac{1}{2}\log\frac{{\tilde L}}{\epsilon}
	\end{equation}
	So we get the usual result
	\begin{equation}
	S=\frac{c}{3}\log\frac{{\tilde L}}{\epsilon}
	\end{equation}

	{\color{red} For TTbar,  \begin{equation}
	S=\frac{c}{3}\int_{- L/2}^{L/2}
		\frac{{\tilde L}/2}{({\tilde L}/2)^2-x^2}dx
		={c\over6} \mop{arctanh} {2x\over {\tilde L}}\bigg|^{L/2}_{-{L/2}}
	\end{equation}   }
	where integration range $L$ is related to $\tilde L$ by requiring that the distance to the pole at $\pm{\tilde L\over 2}$ is cutff
	\eq{
({\tilde L\over 2})^2=2\lambda+({ L\over 2})^2}

@@

	***

	In the thermal CFT$_2$,
	\begin{equation}
	w=e^{\frac{2\pi z}{\beta}}
	\end{equation}
	From this transformation between the cylinder and the plane, we can find the "local" temperature $\tilde{\beta}$
	\begin{equation}
	\tilde{\beta}(x)=2\pi\frac{sinh[\pi(x+l_b)/\beta]sinh[\pi(x-l_b)/\beta]}{sinh(2\pi l_b/\beta)}
	\end{equation}
	After integrating out,
	\begin{equation}
	f(x)=\frac{\log(sinh\frac{\pi(l_b+x)}{\beta})-\log(sinh\frac{\pi(l_b-x)}{\beta})}{2\pi}
	\end{equation}
	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [explain through coordinate map]}
	\begin{equation}
	2l_b=Arccoth(\frac{r_c\cosh(lr_1/2)}{\sqrt{r_1^2+r_c^2\sinh^2(lr_1/2)}})/r_1
	\end{equation}
	where
	\begin{equation}
	r_1=\frac{2\pi}{\beta}
	\end{equation}
	is the outer horizon, and $r_c$ is the cutoff, related to the deformation parameter $\lambda$. The entanglement entropy reads,
	\begin{equation}
	S(L=2l)=\frac{\pi c}{6}(f(l)-f(-l))=\frac{c}{3}\log(\frac{r_c}{r_1}\sinh(l r_1)+\sqrt{1+\frac{r_c^2}{r_1^2}\sinh^2(l r_1)})
	\end{equation}
	The C-function is
	\begin{equation}
	C(l)=lS'(l)=\frac{c}{3}lr_1\coth(lr_1)\sqrt{\frac{r_c^2}{r_c^2+r_1^2csch^2(l r_1)}}
	\end{equation}
	\begin{equation}
	C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}\sqrt{\frac{1}{1+\frac{4\pi^2\epsilon^2}{\beta^2\sinh^2\frac{L\pi}{\beta}}}}
	\end{equation}
	In CFT
	\begin{equation}
	S(L)=\frac{c}{3}\log(\frac{\beta}{\pi \epsilon}\sinh\frac{L\pi}{\beta})
	\end{equation}
	\begin{equation}C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}
	\end{equation}

\section{Bulk story}
	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}. We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity. 
\subsection{Bulk modular flows for Poincar\'e $\mrm{AdS}_3$}
	We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary.

@@

	Alternatively, we can re-derive the bulk modular generator from scratch by requiring that it vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
	}. See \autoref{sect:modFlowPoincare} for a detailed description. 
	Again, the overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon; we demand that the surface gravity is $2\pi$ along the RT surface:
	\begin{equation}
%		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
%	\quad
		\kappa_\xi^2
		= (2\pi)^2
		= -\frac{1}{2}\,
			(\nabla_{\mu} \xi_{\nu})
			(\nabla^{\mu} \xi^{\nu})
	\end{equation}
	Again, we restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{L_\infty}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side ${\tilde L}$. 
	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface.

	{\color{red} use $l_u,\,l_v$}

@@

The RT surface is the set of the fixed points of the modular flow, ....bifurcating surface....

@@

	We note that the $\pdd{z}$ term vanishes in the following two cases:
	\begin{itemize}%[noitemsep,topsep=0pt]
	\item as $z\to 0$, i.e.~near the asymptotic boundary;
	\item within the whole plane: $
			x\sinh\theta
			= t\cosh\theta
		$ where the RT surface lies. 
	\end{itemize}

\subsubsection{Zero temperature: cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}

@@

	This seems nice and all but there is a subtlety for finite cutoff $z = z_c$. 
	In the bulk the constant surface gravity $
		\xi^\nu \cdv{\nu} \xi^\mu
		= \kappa_\xi \xi^\mu
		= 2\pi \xi^\mu
	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$. However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:

	{\color{red} delete
	\begin{equation}
	\begin{aligned}
		\xi^{\mrm{FT}}_c
		\equiv \proj{\text{/\!/}} \xi|_{z_c}
		= \frac{2\pi}{
				\sqrt{1 + (2z_c/L)^2}
			}
		& \bigg\{
			\pqty{
				\pqty{
					(\tfrac{L}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\[-2ex] &\quad 
			+ \pqty{
				\pqty{
					(\tfrac{L}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{equation}
	Which no longer has normalized $\beta$ if $z_c \ne 0$.
}

@@

\subsubsection{Restoring the $2\pi$ periodicity by following the flow}

@@

\pagebreak
\subsection{Gravitational charges}

@@

\subsubsection{Finite temperature: modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
\textbf{Summary:} We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.

@@

\pagebreak
\subsubsection{BTZ with constant cutoff}
\textbf{Summary:} We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}. This gives a finite temperature generalization of the result of \cite{Lewkowycz:2019xse}.

@@

\appendix

\section{Modular flow for Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
\label{sect:modFlowPoincare}

>>>>

\affiliation[a]{Yau Mathematical Sciences Center, Tsinghua University, Beijing 100084, China\ \,\normalsize\ccbyncsajp}

@@

\addtocounter{section}{-1}
\begin{itemize}[nosep]
\item maybe consider later: SSA 
\item maybe consider later: finite size effect  
\end{itemize}

\pagebreak
\section{Conventions}
	We try to follow the conventions of the TsT paper \textcite{Apolo:2019zai}. 
	\begin{itemize}
	\item Lightcone coordinates: $u,v = x\pm t$, similar to \cite{Apolo:2019zai}. This convention has the following features:

@@

\section{Black spectrum from gravitional charges}
	Ref: \textcite{Wald:1993nt,Iyer:1994ys,Iyer:1995kg}, \textcite{Lewkowycz:2013nqa}, and \textcite{Faulkner:2013ana}.

@@

\subsection{Covariant charges}

@@

\subsection{Killing vectors}

@@

	Alternatively, note that we can perform a coordinate transformation 
	 % 
	 \eq{
	 \til{t}  = \frac{\sqrt{f(r_c)}}{r_c} t, \qquad \qquad \til{\phi} = \phi + \frac{4 G J }{r_c^2}t,
	 }
	 %
	to turn the induced metric~\eqref{inducedmetric} into the Minkowski metric,
	  %
	  \eq{
	  ds^2_{c} = r_c^2 \big({- d\til{t}^2} + d \til{\phi}^2 \big ), \label{mink}
	  }
	with the identifications of the original coordinates left intact, i.e.
	  %
	  \eq{
	  (\til{t},\,\til{\phi}) \sim (\tilde{t},\,\til{\phi} + 2 \pi).
	  }
	  %
	We thus find that the Killing vector $\xi_c$ is, up to a normalization, nothing but the generator of time translations in a locally nonrotating frame~\cite{Misner:1974qy},
	  %
	  \eq{
	  \xi_c  = \frac{r_c}{\sqrt{f(r_c)}} \bigg (\p_t - \frac{4 G J}{r_c^2} \p_{\phi} \bigg ) = \p_{\tilde{t}}. \label{xi1}
	  }
	  %

	The Killing vector~\eqref{xi1} satisfies the following properties:
	 %
	 \begin{enumerate}[nosep]
	 \item[(i)] it leads to integrable charges, see eq.~\eqref{quasilocalcharge2};
	 \item[(ii)] its normalization is background-independent and proportional to $r_c^2$;
	 \item[(iii)] it measures the energy of a locally nonrotating observer in the orthonormal frame;
	 \item[(iv)] it reduces to the Killing vector measuring the total (ADM) energy when $r_c \to \infty$.
	 \end{enumerate}

\subsection{Quasilocal energy}

@@

\pagebreak
\section{The boundary story: modular flow \& entanglement entropy}

\subsection{Boundary modular flow}

@@

	For simplicity, we now restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{\tilde{l}}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	We then introduce the \textit{rapidity} $\theta$ to nicely parametrized the boosted interval. For a constant time slice, we have $\theta = 0$. For a general boosted interval, we have:
	\begin{equation}
		x_\pm = \pm \frac{\tilde{l}}{2} \cosh \theta,
	\quad
		t_\pm = \pm \frac{\tilde{l}}{2} \sinh \theta,
	\end{equation}
	Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface. 
	We have:
	\begin{gather}
	\begin{aligned}
		\xi_\mrm{CFT} &= \frac{2\pi}{\tilde{l}} \bigg\{
			\pqty{
				\pqty{
					(\tfrac{\tilde{l}}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\ &\qquad\qquad 
			+ \pqty{
				\pqty{
					(\tfrac{\tilde{l}}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{gather}
	Suppose the interval $\mcal{A}$ lies on the constant $t = 0$ slice; around the constant $t = 0$ slice, the modular flow becomes:
	\begin{equation}
		\xi_\mrm{CFT}|_{t = 0} 
		= \frac{2\pi}{\tilde{l}}
			\pqty{
				(\tfrac{\tilde{l}}{2})^2
				- x^2
			} \,\pdd{t}
	\end{equation}

@@

	For example, for a single interval in CFT$_2$,
	\begin{equation}
		\beta(x)
		= \frac{2\pi}{\tilde{l}}
			\pqty{
				\pqty{\tfrac{\tilde{l}}{2}}^2
				- x^2
			} \,\pdd{t}
	\end{equation}
	\begin{equation}
	S= \frac{c}{3} \int_{-\tilde{l}/2}^{\tilde{l}/2}
			\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx,
	\end{equation}
	The indefinite integral $
		\int \frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
		= \mop{arctanh}\frac{2x}{\tilde{l}}
%		\rightarrow\mrm{CFT}
	$ diverges as $x\rightarrow \tilde{l}/2$, so one needs a cutoff:
	\begin{equation}
	S=\frac{c}{3}\int_{-\tilde{l}/2+\epsilon}^{\tilde{l}/2-\epsilon}
		\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
	=\frac{2c}{3} \mop{arctanh} \pqty{
			1-\frac{2\epsilon}{\tilde{l}}
		}
	\end{equation}
	As $\epsilon\rightarrow 0$,
	\begin{equation}
		\mop{arctanh} \pqty{
			1-\frac{2\epsilon}{\tilde{l}}
		}\rightarrow \frac{1}{2}\log\frac{\tilde{l}}{\epsilon}
	\end{equation}
	So we get the usual result
	\begin{equation}
	S=\frac{c}{3}\log\frac{\tilde{l}}{\epsilon}
	\end{equation}

	{\color{red} For TTbar,  \begin{equation}
	S=\frac{c}{3}\int_{- L/2}^{L/2}
		\frac{\tilde{l}/2}{(\tilde{l}/2)^2-x^2}dx
		={c\over6} \mop{arctanh} {2x\over \tilde{l}}\bigg|^{L/2}_{-{L/2}}
	\end{equation}   }
	where integration range $L$ is related to $\tilde L$ by requiring that the distance to the pole at $\pm{\tilde L\over 2}$ is cutff
	\eq{
({\tilde L\over 2})^2=2\lambda+({ L\over 2})^2}

@@

\pagebreak
\section{Zero temperature: the bulk modular flow for Poincar\'e $\mrm{AdS}_3$}

	We follow the recipe from the swing surface proposal \cite{Apolo:2020bld,Apolo:2020qjm} to extend the boundary modular flow to the bulk, by matching symmetries of the bulk and the boundary. 
	We first compute everything in Poincar\'e $\mrm{AdS}_3$ for simplicity. 
	This reproduces known results in e.g.~\cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm} \sidenote{[more citations needed]}.

@@

	Alternatively, we can re-derive the bulk modular generator from scratch by requiring that it vanishes along the RT surface, i.e.~the RT surface is the fixed point of the modular flow; with this condition we can fix the coefficients of the modular generator, up to an overall coefficient\footnote{
		One can compare this with similar results in the literature such as \cite{Lashkari:2016idm,Czech:2019vih,Apolo:2020qjm}. 
	}. See \autoref{sect:modFlowPoincare} for a detailed description. 
	Again, the overall coefficient of $\xi$ (in this case, $2\pi$) is fixed by normalizing the temperature of the horizon; we demand that the surface gravity is $2\pi$ along the RT surface:
	\begin{equation}
%		\beta_\xi = \frac{2\pi}{\kappa_\xi} = 1,
%	\quad
		\kappa_\xi^2
		= (2\pi)^2
		= -\frac{1}{2}\,
			(\nabla_{\mu} \xi_{\nu})
			(\nabla^{\mu} \xi^{\nu})
	\end{equation}
	Again, we restrict to an interval centered at the origin: $
		u_\pm v_\pm
		= x^2_\pm - t^2_\pm
		= (\frac{L_\infty}{2})^2
	$, where $x_\pm = -x_\mp$, and same for $t_\pm, u_\pm, v_\pm$. 
	$L_\infty$ is the coordinate length of the boundary interval $\mcal{A}$ at the asymptotic infinity; this corresponds to the field theory side $\tilde{l}$. 
	For now the coordinates $u_\pm, v_\pm, x_\pm, t_\pm$ and the coordinate length $L_\infty$ are all specified at $z\to 0$, i.e.~at the \textbf{asymptotic boundary}. Note that the RT surface lies on the plane $
		t_\pm / x_\pm = \tanh \theta
	$, namely $\theta$ is constant along the RT surface.

@@

@@

	We note that the $\pdd{z}$ term vanishes in the following two cases:
	\begin{itemize}[noitemsep,topsep=0pt]
	\item as $z\to 0$, i.e.~near the asymptotic boundary;
	\item within the whole plane: $
			x\sinh\theta
			= t\cosh\theta
		$ where the RT surface lies. 
	\end{itemize}

\subsection{Cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}

@@

	This seems nice and all but there is a subtlety for finite cutoff $z = z_c$. 
	In the bulk the constant surface gravity $
		\xi^\nu \cdv{\nu} \xi^\mu
		= \kappa_\xi \xi^\mu
		= 2\pi \xi^\mu
	$ guarantees that after Wick rotation, the Euclidean periodicity around the horizon is normalized to $\beta = 1$. However, if we restrict to the field theory living at constant cutoff $z = z_c$, which corresponds to a \TTbar deformed theory \cite{McGough:2016lol,Lewkowycz:2019xse} \sidenote{[more citations needed]}, since it has no knowledge of the $\pdd{z}$ component of $\xi$, we should reduce it to a modular flow within the $z = z_c$ plane by, e.g.~projecting the $z$ component out, which leaves us:
	\begin{equation}
	\begin{aligned}
		\xi^{\mrm{FT}}_c
		\equiv \proj{\text{/\!/}} \xi|_{z_c}
		= \frac{2\pi}{
				\sqrt{1 + (2z_c/L)^2}
			}
		& \bigg\{
			\pqty{
				\pqty{
					(\tfrac{L}{2})^2
					- (t^2 + x^2)
				} \cosh\theta
				+ 2tx \sinh\theta
			} \,\pdd{t}
		\\[-2ex] &\quad 
			+ \pqty{
				\pqty{
					(\tfrac{L}{2})^2
					+ (t^2 + x^2)
				} \sinh\theta
				- 2tx \cosh\theta
			} \,\pdd{x}
		\bigg\}
	\end{aligned}
	\end{equation}
	Which no longer has normalized $\beta$ if $z_c \ne 0$.

@@

\subsection{Restore the $2\pi$ periodicity by following the flow}

@@

\pagebreak
\section{Finite temperature: entanglement entropy as gravitational charges}

@@

\subsection{Modular flow in $\mrm{BTZ}_3$ and entanglement entropy}
\textbf{Summary:} We map the the modular flow in the Poincar\'e $\mrm{AdS}_3$ vacuum to the BTZ background, and compute the entanglement entropy as gravitational charge.

@@

\pagebreak
\subsection{BTZ with constant cutoff}
\textbf{Summary:} We then consider constant $r$ cutoff in the Schwarzschild coordinates, which corresponds to the proposal of \cite{McGough:2016lol}. This gives a finite temperature generalization of the result of \cite{Lewkowycz:2019xse}.

@@

\pagebreak
\appendix
\section{Modular flow for Poincar\'e $\mrm{AdS}_3/\mrm{CFT}_2$}
\label{sect:modFlowPoincare}
